---
title: "Basic Stats"
author: "Lilly Winfree & Danielle Robinson"
date: "September 6, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Let's learn how to read in data and then do some basic statistical analysis.
Read in data:

```{r}
data<-read.table("example_lengths_for_R.csv", header=TRUE, sep=',')
```
We can look at the data quickly using summary(), nrow() to see the row numbers, colnames() for column names
```{r}
summary(data)
nrow(data)
colnames(data)
```
We can subset to different columns with $ and only see select rows with [:]
```{r}
data$coverlip.code[1:10]
data$treatment[1:10]
summary(data$values)
summary(data$values[data$treatment=='Control'])
```
Let's plot our data!
```{r}
plot(data$treatment, data$values, xlab='treatment', ylab='length values')
```


Now let's look at how to do some basic stats:
```{r}
mean(data$values[data$treatment=='Treatment A'])
mean(data$values[data$treatment=='Control'])
mean(data$values[data$treatment=='Treatment B'])
median(data$values[data$treatment=='Control'])
var(data$values[data$treatment=='Control'])
min(data$values[data$treatment=='Control'])
max(data$values[data$treatment=='Control'])
```
notice how summary() gave us the same info as the above functions
OK let's do a t-test now! We can use this to compare the means between 2 of the groups
```{r}
t.test(data$values[data$treatment=='Control'], data$values[data$treatment=='Treatment B'])
```
What does this tell us?
How do we change the code to look at the other groups?

We can also do an ANOVA with this data:
```{r}
results=aov(values ~ treatment, data=data)
summary(results)
```
See ANOVA doc for more info on how an ANOVA works.
